Bayesian exponential random graph modelling of KWL Burial network

### 2020-04-03 analysis/paper/paper.Rmd
run Bergm code for post-European successfully, takes ~1 hr
working on archaeological background

The burial data we analyzed in this paper are collected from the upper component of Kiwulan site, an Iron Age settlement site (AD1350-AD1950) located in northeastern Taiwan which experienced the European colonial impacts in the 17th century and the large wave of Chinese immigrants in the 19th century. The burials were assigned to pre-European contact period, post-European contact period, and Chinese period based on the stratigraphic data, radiocarbon dates, and diagnostic porcelain such as white-glazed jars as a time indicator of the arrival of the Europeans[citation]. The excavation revealed abundent pottery sherds, imported ceramics and stonewares, wooden artifacts, stone tools, metal artifacts, imported glass beads and agates beads, and pipes [@Chen2007]. In addition to these artifacts, 90 burials, hundreds of middens, storage pits, and postholes with in-situ posts were also excavated. The burials were mostly located in the AD section, which is the largest open area at Kiwulan site that provides continuous stratigraphic sections suitable for comparison. Those burials are oriented in an east-west direction located on the north side of the house structures indicated by postholes and in-situ wooden posts. Previous research indicates the presence of economic inequality between burials, but there is debate about whether these represent an egalitarian or stratified society [@Cheng2008; @Hsieh2012]. @Cheng2008 interprets the unequal distribution of prestige materials, such as the golden beads, between burials, as evidence for hierarchy. However, @Hsieh2012 suggests a relatively egalitarian form from the comparative analysis of frequency and proportion of burial goods. She finds that the rich burials were usually associated with elders, which might indicate achieved, rather than inherited, status. The use of prestige goods in burials might be traced back before the European arrival according to historical records from Spanish and Chinese [@Borao2009; Li and Wu 2006). If Cheng is correct and socio-economic inequality was present, it might be rooted in the use of prestige goods traded in the area before the Europeans arrived. In this case, pre-existing inequalities might have become more accentuated as a response to European contact. Did the degree of economic inequality change over time, and how did European contact impact indigenous social organization? These questions motivate this project.

@@

## statistics
We want to know

>>>>

The burial data we analyzed in this paper are collected from the upper component of Kiwulan site, an Iron Age settlement site (AD1350-AD1950) located in northeastern Taiwan which experienced the European colonial impacts in the 17th century and the large wave of Chinese immigrants in the 19th century. The excavation revealed abundant pottery sherds, imported ceramics and stonewares, wooden artifacts, stone tools, metal artifacts, imported glass beads and agates beads, and pipes [@Chen2007]. In addition to these artifacts, 90 burials, hundreds of middens, storage pits, and postholes with in-situ posts were also excavated. The burials were mostly located in the AD section, which is the largest open area at Kiwulan site that provides continuous stratigraphic sections suitable for comparison. Those burials are oriented in an east-west direction located on the north side of the house structures indicated by postholes and in-situ wooden posts. Previous research indicates the presence of economic inequality between burials, but there is debate about whether these represent an egalitarian or stratified society [@Cheng2008; @Hsieh2012]. @Cheng2008 interprets the unequal distribution of prestige materials, such as the golden beads, between burials, as evidence for hierarchy. However, @Hsieh2012 suggests a relatively egalitarian form from the comparative analysis of frequency and proportion of burial goods. She finds that the rich burials were usually associated with elders, which might indicate achieved, rather than inherited, status. The use of prestige goods in burials might be traced back before the European arrival according to historical records from Spanish and Chinese [@Borao2009; Li and Wu 2006). Analysing burial data will give an insight into the social reactions of Kiwulan residents and provide a way to examine and explain the changes in social inequality at Kiwulan before and after European contact.

Burials were assigned to pre-European contact period, post-European contact period, and Chinese period based on the stratigraphic data, radiocarbon dates, and diagnostic porcelain such as white-glazed jars as a time indicator of the arrival of the Europeans[citation]. The burials that were disturbed severely due to modern construction are excluded due to incomplete data. Since the accumulation of imported prestige goods in burials is commonly observed, we assign the burials into four classes, high, medium, low, and none, accoutring to the total number of burial goods to indicate the index of wealth.

@@

## Statistics
We want to know
